---
title: "4620Project"
author: "ShiyuDou"
date: "11/25/2020"
output: html_document
---
```{r,include=F}
library(ISLR)
library(tree)
library(randomForest)
library(MASS)
if (!require("splines")) {
install.packages("splines")
library(splines) }
library(tidyverse)
library(readr)
library(lattice)
library(ggplot2)
library(GGally)
```

```{r}
library(readr)
Wage <- read_csv("Wage_Stat4620.csv")
View(Wage)
```


```{r, warning=F}
Wage$maritl = substr(Wage$maritl, 1, 1)
Wage$race = substr(Wage$race, 1, 1)
Wage$education = substr(Wage$education, 1, 1)
Wage$region = substr(Wage$region, 1, 1)
Wage$jobclass = substr(Wage$jobclass, 1, 1)
Wage$health = substr(Wage$health, 1, 1)
Wage$health_ins = substr(Wage$health_ins, 1, 1)
```


```{r, warning=F}
library(tidyverse)
Wage <- Wage %>% 
    mutate(maritl = as.factor(recode(maritl, 
                      "1" = 1, 
                      "2" = 2,
                      "3" = 3,
                      "4" = 4,
                      "5" = 5))) %>% 
    mutate(race = as.factor(recode(race, 
                      "1" = 1, 
                      "2" = 2,
                      "3" = 3)))%>% 
    mutate(education = as.factor(recode(education, 
                      "1" = 1, 
                      "2" = 2,
                      "3" = 3,
                      "4" = 4,
                      "5" = 5)))%>% 
    mutate(region = as.factor(recode(region, 
                      "1" = 1, 
                      "2" = 2)))%>% 
    mutate(jobclass = as.factor(recode(jobclass, 
                      "1" = 1, 
                      "2" = 2)))%>% 
    mutate(health = as.factor(recode(health, 
                      "1" = 1, 
                      "2" = 2)))%>% 
    mutate(health_ins = as.factor(recode(health_ins, 
                      "1" = 1, 
                      "2" = 2)))%>%
  mutate(RespB = as.factor(recode(RespB, 
                      "Yes" = 1, 
                      "No" = 2)))
```

```{r, warning=F}
set.seed(4620)
attach(Wage)
train = sample(1:nrow(Wage), nrow(Wage)/2)
Wage.train = Wage[train, ]
Wage.test = Wage[-train,]
```


```{r}
set.seed(4)
tree.fit = tree(RespB ~ ., data = Wage.train)
summary(tree.fit)
tree.pred = predict(tree.fit, Wage.test)
# Test MSE
mean((tree.pred - Wage.test$Resp)^2)
plot(tree.fit)
text(tree.fit, pretty = 0, cex =1.5)
```

```{r}
imp = mice(Wage_Stat4620, m = 20,printFlag = FALSE, maxit = 40, seed=2525)
fit.mi = with(data=imp, exp = lm(Resp~year+X1+age+logwage+wage,data =Wage_Stat4620))
combFit = pool(fit.mi) 
imp_2 =complete(imp,2)
```

```{r}
imp2 = mice(Wage_Stat4620, m=20,printFlag=FALSE, maxit = 40, seed=2525)
fit.mi2 = with(data=imp2, exp = glm(RespB~year+X1+age+logwage+wage,data =Wage_Stat4620,family = binomial))
combFit = pool(fit.mi2) 
imp_2 =complete(imp,2)
```

2.a.ii exploratory analysis and preprocessing

```{r}
pairs(Wage)

```

```{r}
splom(Wage)
```

```{r}

#plotmatrix(Wage[1:4])

```


2.a.iii Split data into testing set and training set.

```{r}
#Wage
set.seed(4620)
ix=sample(1:nrow(Wage), nrow(Wage)/2)
wage.train=Wage[ix,]
wage.test = Wage[-ix,]

```

Histogram with different marriage status.

```{r}
ggplot2.histogram(data=Wage, xName='Resp',
        groupName='mariti', legendPosition="top")

```

Histogram with different race. 

```{r}
ggplot2.histogram(data=Wage, xName='Resp',
        groupName='race', legendPosition="top")

```

Histogram to compare the Resp value for people with different education status.

```{r}
ggplot2.histogram(data=Wage, xName='Resp',
        groupName='education', legendPosition="top")

```


Histogram to compare the Resp value for people with different jobclass. 

```{r}
ggplot2.histogram(data=Wage, xName='Resp',
        groupName='jobclass', legendPosition="top")

```

Histogram to compare the Resp value for people with different health conditions. 
```{r}
ggplot2.histogram(data=Wage, xName='Resp',
        groupName='health', legendPosition="top")

```

